Using Planning to Generate Natural-Language Sentences:\\ Experiences and Challenges

### 2009-12-18 trunk/Papers/crisp-ff-10/crisp-ff.tex
pre-final version ff-sec
additional cites

Can we design heuristics that are better at deadling with the
lifecycle of substitution nodes and distractors? The problem of not
noticing them in the initial state is present for all approaches that
are dominated by $h^+$,
e.g.\ \cite{karpas:domshlak-ijcai-09,helmert:domshlak:icaps-09}, and
is also present for the known inadmissible landmarks heuristics
\cite{richter:etal:aaai-08}. As far as known heuristics are concerned,
hope thus resides mainly in the $h^m$ family and in abstraction
heuristics. We ran a few tests with an example like the rabbit one,
except that there are 10 distractors. The Graphplan estimate for the
initial state is $4$, i.e., $h^2$ is better than $h^+$ here. Still,
$4$ is far away from the real goal distance $14$. %
%{\bf here I could use
%  differently scaled versions to see whether the distance estimate is
%  constant across the number of distractors; I would think that
%  yes}. 
With merge\&shrink \cite{helmert:etal:icaps07}, we experimented with
various settings for the parameters (number of abstractions and size
limit for each abstraction) but could not find a setting that reduced
the search nodes to less than $5000$. So, all in all, finding better
heuristic functions for this kind of problem remains a challenge.

@@

The only FF technique that appears to work reasonably well is its
action pruning technique, the ``helpful actions''. While the relaxed
plan is often much too short, it appears to always contain at least
one of the actions that actually are useful, and it certainly prunes
the set of avaibale actions quite effectively. For example, in the
10-distractor test instance, $16875$ nodes are explored without
helpful actions pruning; with pruning, this reduces to $3078$. For
larger examples, the factor between the two numbers tends to become
larger. %{\bf here, again, having actual scaled examples would help}
%{\bf use here larger version of
%  modifiers-10-10???}

>>>>

Can we design heuristics that are better at dealing with the lifecycle
of substitution nodes and distractors? The problem of not noticing
them in the initial state is present for all approaches that are
dominated by $h^+$,
e.g.\ \cite{karpas:domshlak-ijcai-09,helmert:domshlak:icaps-09}. The
same problem is also present for the inadmissible landmarks heuristic
\cite{richter:etal:aaai-08}, as well as for $h^{\mathsf{cea}}$
\cite{helmert:geffner:icaps-08} and its variant $h^{\mathsf{pcc}}$
\cite{cai:etal:icaps-09}, and hence also for $h^{\mathsf{CG}}$
\cite{helmert:icaps-04}. As far as known heuristics are concerned,
hope thus resides mainly in the $h^m$ family and in abstraction
heuristics. We ran a few tests with an example like the rabbit one,
except that there are 10 distractors. The Graphplan estimate for the
initial state is $4$, i.e., $h^2$ is better than $h^+$ here. Still,
$4$ is far away from the real goal distance $14$. %
%{\bf here I could use
%  differently scaled versions to see whether the distance estimate is
%  constant across the number of distractors; I would think that
%  yes}. 
% .. have tried IPP on NEUES-MODIFIER-SET but get seg faults and shit..
% oh, whatever.
With merge\&shrink \cite{helmert:etal:icaps07}, we obtained the
estimate $11$ for the initial state, which is much better. Still, we
could not find a parameter setting that reduced the search nodes to
less than $5200$, which is not much better than blind search which
took $13800$ nodes. So, all in all, finding better heuristic functions
for this kind of problem remains a challenge.

@@

%NEUES-MODIFIER-SET$ ../ff -o modifiers-5-5-domain.lisp  -f modifiers-5-5-problem.lisp -T -H: 102
%NEUES-MODIFIER-SET$ ../ff -o modifiers-5-5-domain.lisp  -f modifiers-5-5-problem.lisp -T -H -N: 282
%NEUES-MODIFIER-SET$ ../ff -o modifiers-10-10-domain.lisp  -f modifiers-10-10-problem.lisp -T -H: 3078
%NEUES-MODIFIER-SET$ ../ff -o modifiers-10-10-domain.lisp  -f modifiers-10-10-problem.lisp -T -H -N: 16875
%NEUES-MODIFIER-SET$ ../ff -o modifiers-15-15-domain.lisp  -f modifiers-15-15-problem.lisp -T -H: ?? sehr lange
%NEUES-MODIFIER-SET$ ../ff -o modifiers-15-15-domain.lisp  -f modifiers-15-15-problem.lisp -T -H -N: ?? sehr lange

The only FF technique that appears to work reasonably well is its
action pruning technique, the ``helpful actions''. While the relaxed
plan is often much too short, it appears to always contain at least
one of the actions that actually are useful, and it certainly prunes
the set of avaibale actions quite effectively. For example, in the
10-distractor test instance, $16875$ nodes are explored without
helpful actions pruning; with pruning, this reduces to $3078$. For
larger examples, the factor between the two numbers tends to become
larger.
